\documentclass[essd]{copernicus}

\begin{document}

\title{A 48-member perturbed-physics ensemble of 1/8\degree{} terrestrial water budget data over the conterminous United States, 1980--2015}

\Author[1]{Hui}{Zheng}
\Author[2]{Zong-Liang}{Yang}
\Author[1,3]{Wenli}{Fei}
\Author[4,2]{Peirong}{Lin}
\Author[2]{Wen-Ying}{Wu}
\Author[5,2]{Jiangfeng}{Wei}
\Author[6,2]{Lingcheng}{Li}
\Author[7,2]{Long}{Zhao}
\Author[1]{Kai}{Li}

\affil[1]{Key Laboratory of Regional Climate-Environment Research for Temperate East Asia, Institute of Atmospheric Physics, Chinese Academy of Sciences, Beijing, 100029, China}
\affil[2]{Department of Geological Sciences, John A. and Katherine G. Jackson School of Geosciences, The University of Texas at Austin, Austin, Texas, 78705, USA}
\affil[3]{University of Chinese Academy of Sciences, Beijing, 100049, China}
\affil[4]{Institute of Remote Sensing and Geographic Information System, School of Earth and Space Sciences, Peking University, Beijing, 100871, China}
\affil[5]{Collaborative Innovation Center on Forecast and Evaluation of Meteorological Disasters/Key Laboratory of Meteorological Disaster, Ministry of Education/International Joint Research Laboratory on Climate and Environment Change, Nanjing University of Information Science and Technology, Nanjing, 210044, China}
\affil[6]{Pacific Northwest National Laboratory, Richland, Washington, 99354, USA}
\affil[7]{School of Geographical Sciences, Southwest University, Chongqing, 400715, China}

\correspondence{Zong-Liang Yang (\href{mailto:liang@jsg.utexas.edu}{liang@jsg.utexas.edu})}

\runningtitle{NLDAS-NoahMP perturbed-physics ensemble hydrological data}

\runningauthor{Zheng, Yang, Fei, et al.}

\firstpage{1}

\maketitle


\begin{abstract}

Terrestrial water budget (TWB) data over large domains are of high interest for
various hydrological applications. Land surface model (LSM) ensembles are
well-suited for a spatiotemporally continuous and physically consistent
estimation. As an augmentation of the operational North American Land Data
Assimilation System phase 2 (NLDAS\nobreakdash-2) four-LSM ensemble, this study
presents a 48-member perturbed-physics ensemble configured from the Noah LSM
with multi-physics options (Noah-MP). The forty-eight Noah-MP physics
configurations are selected to give a representative cross-section of commonly
used LSMs for parameterizing runoff, near-surface atmospheric turbulence, soil
moisture limitation on leaf stomata, and stomatal conductance.

Simulation of the ensemble reproduced 1980–2015 monthly TWB over the
conterminous United States at a 1/8° spatial resolution. Total and the
constitutes of evapotranspiration (i.e., canopy evaporation, soil evaporation,
and transpiration) and runoff (i.e., the surface and subsurface components) are
freely downloadable at \url{https://doi.org/place-holder-nmpens-pretrn}.
Terrestrial water storage and its components (i.e., snow water equivalent,
four-layer soil water content from the ground down to 2-m depth, and groundwater
storage anomaly) are retrievable from
\url{https://doi.org/place-holder-nmpens-tws}.

Inter-comparisons and evaluations of the ensemble reconstructions show a larger
ensemble size and would facilitate a better quantification and process-level
attribution of the reconstruction uncertainty. The others include: (1) improved
performance, (2) updated quantification of reconstruction uncertainty, (3)
process-level attribution of the estimation uncertainty.

\end{abstract}


\introduction \label{sec:intro}

Estimates of terrestrial water budget (TWB) over continental domains are of high
interest for a broad range of hydrological applications. Publicly available data
have been applied to investigate the state of the terrestrial water cycle
\citep{trenberth2013GRL, rodell2015JC, scanlon2018P, yin2020HESS,
pascolini-campbell2021N}, to understand the interactions among hydrological
processes, vegetation, climate, and human activities \citep{trenberth2013JC,
lafontaine2015JAWRA, ward2014PNAS, levia2020NG}, to examine the availability and
variability of water resources and use \citep{wu2021JH, hejazi2014HESS,
scanlon2012P, voss2013WRR, lv2019JGRA, le2011P, rodell2009N}, and to assess the
risk of extreme events such as droughts \citep{peters-lidard2021BAMS,
prudhomme2014P, dai2013NCC, su2021JH} and floods \citep{emerton2017NC,
lin2018JH}. With the expanding applications, the availability of TWB datasets
has been rapidly increasing \citep{peters-lidard2018MM, saxe2021HESS,
zhang2018HESS}.

Commonly used methods of estimating TWB include remote sensing, in-situ
observations, and model simulations \citep{saxe2021HESS, mccabe2017HESS,
pan2012JC, gao2010IJRS, trenberth2007JH}. Among these methods, land surface
models (LSMs) are apt for continuously producing physically consistent TWB over
a large domain and long period. These characteristics are particularly favorable
for some circumstances. LSMs could estimate various TWB components
simultaneously, whereas, for some components, such as runoff \citep{lin2019WRR,
beck2017HESS}, root-zone soil moisture \citep{xia2015JHa, xia2015JH}, and
transpiration \citep{lian2018NCC}, direct remote sensing is either unavailable
or highly uncertain. In remote or topographically complex regions, LSMs are
valuable as in-situ observations are sparse \citep{kim2021TC}. Estimation based
on remote sensing and in-situ observations is often impeded by scale mismatch
and observation gaps, whereas the issues impair LSM simulations less. Besides,
LSM simulations are well complementary to remote sensing and in-situ
observations. Combinations of the estimates from different techniques can
improve the estimation accuracy \citep{zhang2018HESS, pan2012JC}, whereas
comparisons between the model-simulated estimates and observations could reveal
the impacts of human activities \citep{zaussinger2019HESS} and underground
processes \citep{zheng2020JAMES}.

For delivering consistent and continuous TWB estimates over a large domain,
several operational multi-LSM ensemble simulation systems have been set up
\citep{xia2019JMR, shi2011SCES, carrera2015JH, rodell2004BAMS}. The North
American Land Data Assimilation System (NLDAS) \citep{xia2012JGRA, xia2012JGRAa,
mitchell2004JGRA} stands as one of the pioneering and most successful systems.
The NLDAS phase 2 (NLDAS\nobreakdash-2) operates over the conterminous United
States (CONUS) from 1979 to near real-time at a spatial resolution of 1/8°. The
system generates a set of multi-source synthesized data of surface meteorology,
vegetation, and soils and uses them to drive an ensemble of four different LSMs.
The four LSMs, namely Noah version 2.8 \citep{ek2003JGRA, chen2001MWR,
chen2001MWRa, chen1997BM}, Variable Infiltration Capacity (VIC) version 4.0.3
\citep{liang1994JGRA}, Mosaic \citep{koster1992JGRA}, and Sacramento Soil
Moisture Accounting (SAC) \citep{burnash1973}, are selected to give a good
cross-section of diverse LSMs with different physical parameterizations
\citep{mitchell2004JGRA}. The models have varying strengths and weaknesses in
process parameterizations and modeling skills \citep{kumar2017WRR}. An ensemble
of multiple models could produce an aggregated estimate that outperforms most of
the ensemble constitutes \citep{fei2021WRR, beck2017HESS, guo2007QJRMS,
ajami2007WRR} as well as quantify the estimation uncertainty resulted from
different model formulations \citep{troin2021WRR, cloke2009JoH}. Evaluations of
the NLDAS\nobreakdash-2 four-LSM ensemble estimates have shown satisfactory
performance in matching the observed evapotranspiration \citep{zhang2020AFM,
xia2012JGRA, kumar2018RS}, runoff \citep{xia2012JGRAa}, soil moisture
\citep{xia2015JH, xia2015JHa}.

This study enriches the NLDAS\nobreakdash-2 four-model ensemble with forty-eight
perturbed-physics configurations of the Noah LSM with multi-physics options
(Noah-MP) citep{niu2011JGRA, yang2011JGRA}. Noah-MP has more physically
realistic representations of the vertical stratification than the
NLDAS\nobreakdash-2 models have. A column of the land in Noah-MP consists of a
vegetation canopy layer, three snowpack layers, four soil layers, and a
groundwater component \citep{niu2011JGRA}. Conceptual (e.g., the five water
tanks of SAC) and lumped (e.g., the vegetation-soil combined surface layer of
Noah) representations of the stratification of vegetation and soil, as used in
the NLDAS\nobreakdash-2 models, are minimized. Noah-MP has a more comprehensive
representation of various land surface processes that are evident at different
depths. The modeled processes include snow accumulation and ablation,
infiltration, percolation, retention, freezing/thawing of snow/soil water,
groundwater recharge/discharge, and energy constraints \citep{niu2011JGRA}. The
improvements in vertical stratification and process parameterizations are
expected to produce better TWB estimates. Previous comparisons between Noah-MP
and the four NLDAS\nobreakdash-2 LSMs have shown that Noah-MP is comparable or
better in estimating soil moisture \citep{cai2014JGRAa}, runoff
\citep{fei2021WRR, cai2014JGRAa}, and evapotranspiration \citep{zhang2020AFM}.
The results encouraged computationally expensive runs of Noah-MP as done in this
study.

The enrichment also features a single-model perturbed-physics ensemble, which is
different from the widely-used multi-model ensembles. The Noah-MP ensemble is
constructed by shuffling the available parameterization options of several
selected processes. The ensemble size grows exponentially as a multiplication of
the available parameterization options of different processes
\citep{yang2011JGRA, zhang2016JGRA, gan2019WRR}. A large ensemble should give a
broad cross-section of feasible model formulations to account for the model
uncertainty in TWB estimation \citep{telteu2021GMD, mitchell2004JGRA} and is
critical for a statistically reliable estimation of the probability of
hydrological events such as floods and droughts \citep{troin2021WRR}. The
single-model perturbed-physics ensemble also facilitates uncertainty attribution
and reduction. The ensemble consists of pairs that are different in the
parameterization of one process and the same in the other processes. The impacts
of the process’s parameterizations can be pinpointed from the model predictive
variations. Variance analysis can be applied to quantify the contribution of the
parameterization of the process and compare the relative importance of two
processes \citep{clark2011WRR, zheng2019WRR}. The quantification could inform
further model development to reduce the model uncertainty. However, there are
pitfalls unique to the single-model perturbed-physics ensemble. The ensemble
members share a significant portion of the same model formulations
\citep{fei2021WRR}. The physics similarity among the ensemble members may
create redundant information and lower the efficiency characterized by the ratio
of ensemble utility over computational costs. Future development of ensemble
aggregation and optimization methods should be developed for the single-model
perturbed-physics ensemble. A publically available dataset would promote the
studies.

We will show the information necessary for using the dataset in
Section~\ref{sec:data}, including the dataset variables, file organizations, and
the source data and models used for data generation. In this study, we will
focus on the assessment of data performance and uncertainty. The assessment
methods are described in Section~\ref{sec:evaluation}, and
Section~\ref{sec:result} presents the assessment results. The results could
directly inform applications of the data. After Section~\ref{sec:availability}
shows the data availability, Section~\ref{sec:conclusion} provides conclusions
and discussions.


\section{Dataset description} \label{sec:data}

The dataset contains gridded surface energy and water budget variables over the
CONUS. Section~\ref{sec:data:variables} describes the dataset variables and
their physical relationships. The forty-eight Noah-MP physics configurations
used to create the dataset are detailed in Section~\ref{sec:data:noahmp}.
Sections~\ref{sec:data:nldas} and \ref{sec:data:simulation} brief the
atmospheric forcing, static parameters of vegetation and soil, and simulation
settings.


\subsection{Dataset variables} \label{sec:data:variables}

Table~\ref{tbl:variables} lists the dataset variables. The variables are
available at each 1/8° NLDAS\nobreakdash-2 grid indicated by a land-water mask
($X$). The variables fall into two groups: the surface water and energy budget
variables.

\begin{table}[t]
    \caption{The dataset variables.}
    \label{tbl:variables}
    \centering
    \begin{tabular}{lll}
        \tophline
        Symbol       & Units                   & Description                                \\
        \middlehline
        \multicolumn{3}{c}{surface water budget}                                            \\
        $E$          & \unit{kg~m^{-2}~s^{-1}} & total evapotranspiration                   \\
        $E_{can}$    & \unit{kg~m^{-2}~s^{-1}} & evaporation of canopy interception         \\
        $E_{gnd}$    & \unit{kg~m^{-2}~s^{-1}} & direct evaporation from the ground         \\
        $E_{tran}$   & \unit{kg~m^{-2}~s^{-1}} & transpiration                              \\
        $R$          & \unit{kg~m^{-2}~s^{-1}} & total runoff                               \\
        $R_{srf}$    & \unit{kg~m^{-2}~s^{-1}} & surface runoff                             \\
        $R_{und}$    & \unit{kg~m^{-2}~s^{-1}} & subsurface runoff                          \\
        $W$          & \unit{kg~m^{-2}}        & terrestrial water storage                  \\
        $W_{can}$    & \unit{kg~m^{-2}}        & canopy interception                        \\
        $W_{snow}$   & \unit{kg~m^{-2}}        & snow water equivalent                      \\
        $W_{gw}$     & \unit{kg~m^{-2}}        & unconfined groundwater storage             \\
        $w_{soil,i}$ & \unit{m^3~m^{-3}}       & volumetric soil water content              \\
        [1mm]
        \multicolumn{3}{c}{surface energy budget}                                           \\
        $S$          & \unit{W~m^{-2}}         & absorbed solar radiation                   \\
        $S_{can}$    & \unit{W~m^{-2}}         & canopy absorbed solar radiation            \\
        $S_{gnd}$    & \unit{W~m^{-2}}         & ground absorbed solar radiation            \\
        $I$          & \unit{W~m^{-2}}         & net longwave radiation                     \\
        $I_{can}$    & \unit{W~m^{-2}}         & net longwave radiation at the canopy       \\
        $I_{gnd}$    & \unit{W~m^{-2}}         & net longwave radiation at the ground       \\
        $H$          & \unit{W~m^{-2}}         & sensible heat flux                         \\
        $H_{can}$    & \unit{W~m^{-2}}         & sensible heat flux from the canopy         \\
        $H_{gnd}$    & \unit{W~m^{-2}}         & sensible heat flux from the ground         \\
        $T_{snow,j}$ & \unit{K}                & snow layer temperature ($0 \leq j \leq 3$) \\
        $T_{soil,i}$ & \unit{K}                & soil layer temperature ($i=1,\dots,4$)     \\
        [1pt]
        \multicolumn{3}{c}{auxiliary variables}                                             \\
        $X$          & \unit{-}                & land-water mask                            \\
        \bottomhline
    \end{tabular}
\end{table}


\subsubsection{surface water budget}

Neglecting horizontal water exchange between adjacent grid, the water budget
closure could be obtained among the precipitation ($P$,
\unit{kg~m^{-2}~s^{-1}}), evapotranspiration ($E$), runoff ($R$), and
terrestrial water storage ($W$) change \citep{zheng2020JAMES}:
\begin{equation}
    P = E + R + \Delta W \text{,}
\end{equation}
where, precipitation ($P$) is from NLDAS\nobreakdash-2 (described in
Sections~\ref{sec:data:nldas}) and used as model input in this study.

Noah-MP resolves the constitutes of the water budget terms. Evapotranspiration
($E$) consists of canopy evaporation ($E_{can}$), ground evaoration ($E_{gnd}$),
and transpiration ($E_{tran}$):
\begin{equation}
    E = E_{can} + E_{gnd} + E_{tran} \text{.}
\end{equation}
Runoff {$R$} is the sum of a surface and subsurface component:
\begin{equation}
    R = R_{srf} + R_{und} \text{.}
\end{equation}
Terrestrial water storage ($W$) consists of canopy interception ($W_{can}$),
snow water equivalent ($W_{snow}$), groundwater storage in unconfined aquifers
($W_{gw}$), and soil water content in four layers ($W_{soil,i}$,
\unit{kg~m^{-2}}):
\begin{equation}
    W = W_{can} + W_{snow} + W_{gw} + \sum_{i=1}^{N_{soil}} W_{soil,i} \text{,}
\end{equation}
where $N_{soil} = 4$ is the number of soil layers.
Soil water storage ($W_{soil,i}$) is not provided in the dataset but can be
calculated from volumetric soil water content ($w_{i}$):
\begin{equation}
    W_{soil,i} = \rho_{wat} w_i \Delta z_{soil,i}
    \quad \text{for} \; i = 1,\dots,N_{soil}
    \text{,} \label{eq:soil-vmc}
\end{equation}
where $\rho_{wat}=1000$\,\unit{kg~m^{-3}} is the density of water; $\Delta
z_{soil,1}=0.1$\,\unit{m}, $\Delta z_{soil,2}=0.3$\,\unit{m}, $\Delta
z_{soil,3}=0.6$\,\unit{m}, and $\Delta z_{soil,4}=1.0$\,\unit{m} are the thickness
of the four soil layers.

\subsubsection{surface energy budget}

Assuming that there is no horizontal energy exchange, the surface energy budget
of a grid cell is closed as follow:
\begin{equation}
    R_n = S + I = H + L + \Delta U \text{,} \label{eq:energy-balance}
\end{equation}
where $R_n$ is net radiation, $S$ is absorbed solar radiation, $I$ is net
longwave radiation, $H$ is sensible heat flux, $L$ is latent heat flux, and
$\Delta U$ (\unit{J~m^{-2}~s^{-1}}) is internal energy change of the land
column. The reflected solar ($S_u$, \unit{W~m^{-2}}) and emitted longwave
($I_u$, \unit{W~m^{-2}}) is not included in the dataset but can be calculated
using the NLDAS\nobreakdash-2 downward solar ($S_u$, \unit{W~m^{-2}}) and
longwave ($I_u$, \unit{W~m^{-2}}) radiation data:
\begin{align}
    S_u = & S_d - S \text{,} \\
    I_u = & I_d - I \text{.}
\end{align}

The energy budget terms consist of two components for the vegetation canopy and
ground.
\begin{align}
    S = & S_{can} + S_{gnd} \text{,} \\
    I = & I_{can} + I_{gnd} \text{,} \\
    H = & H_{can} + H_{gnd} \text{,} \\
    L = & L_{can} + L_{gnd} \text{,}
\end{align}
where $S_{can}$ ($S_{gnd}$) is the absorbed solar radiation at the canopy
(ground), $I_{can}$ ($I_{gnd}$) is the net longwave radiation at the canopy
(ground), $H_{can}$ ($H_{gnd}$) is the sensible heat flux from the canopy
(ground). $L_{can}$ is the latent heat flux from the canopy and linked to the
processes of interception evaporation ($E_{can}$) and transpiration
($E_{tran}$). $L_{gnd}$ is the latent heat flux from the ground and associated
with ground evaporation ($E_{gnd}$). The energy budget terms of the canopy and
ground are both balanced:
\begin{align}
    S_{can} + I_{can} = & H_{can} + L_{can} \text{,}            \\
    S_{gnd} + I_{gnd} = & H_{gnd} + L_{gnd} + \Delta U \text{.}
\end{align}

The change in internal energy ($\Delta U$) is attributed to the temperature
change and water freezing/melting of the land column:
\begin{multline}
    \Delta U = \sum_{j=1}^{N_{snow}} c_{snow,j} \Delta z_{snow,j} \Delta T_{snow,j} \\
    + \sum_{i=1}^{N_{soil}} c_{soil,i} \Delta z_{soil,i} \Delta T_{soil,i}
    + \Delta U_{melt} \text{,}
\end{multline}
where $0<=N_{snow}<=3$ is the number of snow layers, $T_{snow,j}$ is the
temperature of the $j$-th snow layer (\unit{K}), $\Delta z_{snow,j}$ is the
thickness of $j$th snow layer (\unit{m}), $T_{soil,i}$ is the temperature of the
$i$-th soil layer (\unit{K}), and $\Delta U_{melt}$ is the latent heat of water
freezing/melting within the whole land column (\unit{J~m^{-2}~s^{-1}}).
$c_{snow,j}$ is the volumetric heat capacity of the $j$-th snow layer
(\unit{J~m^{-3}~K^{-1}}) and derived from the specific heat capacity of snow ice
($C_{ice} = 2.108 \times 10^3$\,\unit{J~kg^{-1}~K^{-1}}) and supercoolded water
($C_{wat} = 4.188 \times 10^3$\,\unit{J~kg^{-1}~K^{-1}}) as follows:
\begin{equation}
    c_{snow,j} = C_{ice} \rho_{ice} w_{ice,j} + C_{wat} \rho_{wat} w_{liq,j} \text{,}
\end{equation}
where $\rho_{ice} = 916.2$\,\unit{kg~m^{-3}} is the density of ice. $w_{ice,j}$
is the volumetric snow ice content (\unit{m^3~m^{-3}}), $w_{liq,j}$ is the
volumetric liquid water content (\unit{m^3~m^{-3}}). $c_{soil,i}$ is the
volumetric heat capacity of the $i$-th soil layer (\unit{J~m^{-3}~K^{-1}}),
which is a mixture of dry soil matter, water, ice, and air.
\begin{multline}
    c_{soil,i} = c_{mine} (1 - w_{max,i}) \\
    + C_{ice} \rho_{ice} w_{ice,i} + C_{wat} \rho_{wat} w_{liq,i} \\
    + C_{p,air} \rho_{air} (w_{max,i} - w_{ice,i} - w_{liq,i}) \text{,}
\end{multline}
where $w_{max,i}$ is soil porosity (\unit{m^3~m^{-3}}), $C_{p,air} =
1004.64$\,\unit{J~kg^{-1}~K^{-1}} is the isobaric heat capacity of dry air,
$\rho_{air}$ (\unit{m}) is the density of air. $c_{mine}$ is the volumetric heat
capacity of dry soil matter (\unit{J~m^{-3}~K^{-1}}), whose value is
$2\times10^6$ in Noah-MP. $w_{ice,i}$ and $w_{liq,i}$ are the volumetric content
of frozen and liquid water (\unit{m^3~m^{-3}}), respectively, and their sum is
the volumetric water content ($w_{i}$) shown in equation~(\ref{eq:soil-vmc})
(i.e., $w_{i} = w_{ice,i} + w_{liq,i}$).


\subsection{Forty-eight Noah-MP physics configurations} \label{sec:data:noahmp}

The Noah-MP LSM version 3.6 is used in this study. The forty-eight physics
configurations are generated by combining four runoff parameterizations, two
parameterizations of stomatal conductance, three parameterizations of soil
moisture limitation on photosynthesis, and two parameterizations of near-surface
atmospheric turbulence (i.e., $48 = 4 \times 2 \times 3 \times 2$). While
\citet[Table 1]{zheng2019WRR} have listed the used parameterizations, the
following sections will detail the formulations.

\subsubsection{The SIMGM runoff parameterization}

The SIMGM scheme parameterize the surface runoff based on TOPMODEL.

\begin{align}
    R_{srf} =   & Q_{gnd} [(1 - f_{frz,1}) f_{sat} + f_{frz,1} ] \text{,}                          \\
    f_{sat} =   & f_{sat,max} \exp(-0.5 f (z_{wt} - z_{bot})) \text{,}                             \\
    f_{frz,i} = & \exp\left(-\alpha(1 - \frac{w_{ice,1}}{w_{max,1}})\right) - e^{-\alpha} \text{,}
\end{align}

\begin{align}
    R_{sub} =     & (1 - f_{frz,max}) R_{sub,max} e^{-\Lambda - f(z_{wt} - z_{bot})} \text{,} \\
    f_{frz,max} = & \max_{i=1,\dots,N_{soil}} f_{frz,i} \text{,}
\end{align}

$R_{sub,max} = 5$\,\unit{kg~m^{-2}~s^{-1}}, $\Lambda = 10.5$ is the
grid-cell-mean topographic index.


\subsubsection{The SIMTOP runoff parameterization}

\begin{equation}
    f_{sat} = f_{sat,max} \exp(-0.5 f z_{wt}) \text{,}
\end{equation}

$f=2$


\subsubsection{The NOAHR Runoff parameterization}

\begin{align}
    R_{srf} = & Q_{gnd} - Q_{in} \text{,}                                                              \\
    Q_{in} =  & Q_{gnd} \frac{w_d [1-\exp(-k\Delta t)]}{Q_{gnd} + w_d [1 - \exp(-k\Delta t)]} \text{,} \\
    w_d =     & \sum_{i=1}^{N_{soil}} (w_{sat,i} - w_i) \Delta z_{soil,i} \text{,}
\end{align}


\subsubsection{The BATS Runoff parameterization}
\begin{align}
    R_{srf} = & Q_{gnd} \left[ (1 - f_{frz,1}) f_{sat} + f_{frz,1} \right] \text{,}                                                 \\
    f_{sat} = & \theta^4 \text{,}                                                                                                   \\
    \theta =  & \frac{\sum_{i=1}^{N_{soil}}\frac{w_i}{w_{sat,i}}\Delta z_{soil,i}}{\sum_{i=1}^{N_{soil}}\Delta z_{soil,i}} \text{,}
\end{align}




\subsubsection{The Ball-Berry scheme of stomatal conductance}


\subsubsection{The Jarvis scheme of stomatal conductance}


\subsubsection{The three parameterizations of soil moisture limitation on photosynthesis}

\begin{equation}
    \beta = \sum_{i=1}^{N_{root}} \frac{\Delta z_{soil,i}}{z_{root}}
    \min\left(1, \frac{w_{liq,i} - w_{wilt}}{w_{ref} - w_{wilt}}\right)
    \text{,}
\end{equation}

\begin{equation}
    \beta = \sum_{i=1}^{N_{root}} \frac{\Delta z_{soil,i}}{z_{root}}
    \min\left(1, \frac{\psi_{wilt} - \psi_{i}}{\psi_{wilt} - \psi_{sat}}\right)
    \text{,}
\end{equation}

\begin{equation}
    \beta = \sum_{i=1}^{N_{root}} \frac{\Delta z_{soil,i}}{z_{root}}
    \min\left(1, 1 - e^{-c^2 \ln\left(\frac{\psi_{wilt}}{\psi_{i}} \right)} \right)
    \text{,}
\end{equation}


\subsubsection{The Chen97 scheme of near-surface turbulence}

\begin{align}
    \begin{split}
        C_h = & \kappa^2 \left[ \ln\left(\frac{z}{z_{0m}}\right)
            - \Psi_{m}\left(\frac{z}{L}\right)
            + \Psi_{m}\left(\frac{z_{0m}}{L}\right) \right]^{-1} \\
        & \left[ \ln\left(\frac{z}{z_{0h}}\right)
            - \Psi_{h}\left(\frac{z}{L}\right)
            + \Psi_{h}\left(\frac{z_{0h}}{L}\right) \right]^{-1} \text{,}
    \end{split}                                      \\
    z_{0h} = & z_{0m} \exp\left(-\kappa C \sqrt{\text{Re}^*}\right)
\end{align}


\subsubsection{The M-O scheme of near-surface turbulence}

\begin{align}
    \begin{split}
        C_h = & \kappa^2 \left[ \ln\left(\frac{z-d_0}{z_{0m}}\right)
            - \Psi_{m}\left(\frac{z-d_0}{L}\right) \right]^{-1} \\
        & \left[ \ln\left(\frac{z-d_0}{z_{0h}}\right)
            - \Psi_{h}\left(\frac{z-d_0}{L}\right) \right]^{-1}
        \text{,}
    \end{split}      \\
    z_{0h} = & z_{0m} = 0.65 z_{ct}
\end{align}


\subsection{NLDAS-2 atmospheric forcing and static parameters} \label{sec:data:nldas}

Static parameters

Atmospheric forcings

The Noah-MP LSM version 3.6 is used.

Details of the NLDAS multi-model ensemble can be found in
\citet{xia2012JGRA,xia2012JGRAa,fei2021WRR}.

Details of the Noah-MP multi-parameterization ensemble can be found in
\citet{zheng2019WRR,zheng2020JAMES,fei2021WRR}.


\subsection{Simulation settings} \label{sec:data:simulation}


\section{Evaluation and intercomparison methods} \label{sec:evaluation}


\section{Results} \label{sec:result}

\subsection{Spread}

\subsection{Performance}
Biases have been evaluated by \citet{zheng2020JAMES}.

\subsubsection{Terrestrial water storage}

\citep{landerer2012WRR}


\subsubsection{Evapotranspiration}

\subsubsection{Runoff}


\codedataavailability{ The data are freely available for download from the
Zenodo online repository at \url{https://doi.org/place-holder-nmpens-pretrn} and
\url{https://doi.org/place-holder-nmpens-tws}. The dataset (along with datasets
on which it is based) is subject to a Creative Commons BY (attribution) license
agreement (\url{https://creativecommons.org/licenses}, last access:
2021-08-16).} \label{sec:availability}


\conclusions[Conclusions and Discussion] \label{sec:conclusion}
conclusion text


\authorcontribution{ ZLY initiated and funded the study. HZ conducted the
simulation and generated the data. WF contributed to the generation of the
figures. WYW, PL, and JW contributed to the validation of the data. All authors
contributed to the drafting of the manuscript.} \label{sec:contribution}


\competinginterests{The authors declare that they have no conflict of interest}

\disclaimer{The data are provided as-is with no warranties.}

\begin{acknowledgements}

This work is supported by the National Science Foundation of China (grants
42075165, 41375088, and 41605062).

\end{acknowledgements}


%% REFERENCES
\bibliographystyle{copernicus}
\bibliography{library.bib}

\end{document}
